---
title: ""
output: 
    html_document:
      plots: 
        style: Normal
        align: right
    fig_caption: TRUE
    df_print: kable
    fig_height: 2.5
    fig_width: 4
always_allow_html: TRUE
editor_options: 
  chunk_output_type: console
---
[//]: # CSS style arguments

<style type="text/css">

@import url("https://fonts.googleapis.com/css?family=Open+Sans:400,400i,700,700i&display=swap");

h1, h2, h3, h4, h5, body, ul, ol, p, td, th {
font-family: 'Open Sans', sans-serif;

}


body{ /* Normal  */
      font-size: 20px;
      counter-reset:table figure;
  }

.table{
  width:auto;
  font-size:12px;
}

td, th{
  padding-left:10px;
  text-align: right;
  font-family: 'Open Sans', sans-serif;
}

caption::before{
  counter-increment: table;
  content: "Table " counter(table) ": ";
}

.caption::before{
  counter-increment: figure;
  content: "Figure " counter(figure) ": ";
}

caption, .caption{
  font-style:italic;
  font-size: 16px;
  margin-top:0.5em;
  margin-bottom:0.5em;
  width:80%;
  text-align: left;
}

#TOC {
  font-size: 17px;
  width: 100%;
}

</style>

```{r setup, include=FALSE}

# You can set a default figure size here so you don't have to customize every time
knitr::opts_chunk$set(fig.width=8, fig.height=6, warning=FALSE, message=FALSE, cache=FALSE, echo=FALSE)

```

```{r}

# '# PROLOG   ##################################################################'
# '#                                                                           #'
# '# PROJECT: EHDI                                                             #'
# '# PURPOSE: To create visualizations for earlyhearinglossdata website        #'
# '# DIR:     Box\CPHSS\EHDI Seeser\Data\Scripts                               #'
# '# RPRJ:    Box\CPHSS\EHDI Seeser\Data\Data.Rproj                            #'
# '# DATA:    Box\CPHSS\EHDI Seeser\Data\website_ready_data                    #'
# '# AUTHOR:  Veronica L Chaitan                                               #'
# '# CREATED: Aug 09, 2023                                                     #'
# '# LATEST:  SEP 09, 2023                                                     #'
# '# NOTES:                                                                    #'
# '#                                                                           #'
# '# PROLOG   ##################################################################'


library(readxl)
library(htmltools)
library(crosstalk)
library(plotly)
library(kableExtra)
library(magrittr)
library(tidyverse)

# for NA in kable
options(knitr.kable.NA = "")

# Theme settings
# theme_set(theme_minimal()) - doesn't carry over across chunks in RMD
# In general
mytheme <- theme_minimal() + 
  theme(text = element_text(size=11, color="gray23"),
        panel.grid = element_blank(),
        axis.text.x = element_text(size=8, color="gray23"),
        axis.text.y = element_text(size=10, color="gray23"),
        axis.title = element_blank(),
        plot.title = element_blank(),
        legend.position = "top",
        legend.title = element_blank())

# Read in the latest dataset
r <- read_csv("../website_ready_data/ehdidata_2014to2020_cleaned20230908.csv")

# Descriptive table information
vardesc <- read_xlsx("../website_ready_data/variableDescriptionsForWebsite_v1.xlsx")

# Read in the states to get states abbr
states <- read_csv("../website_ready_data/states.csv")

# Read in the descriptive table

# Order the states
r <- r %>%
  mutate(State = factor(State,
                        levels=c("National Average",sort(unique(states$State))))) 

# State codes
r <- r %>%
  # Joining with `by = join_by(State)`
  left_join(states)


# Long format for mapping
r1 <- r %>% 
  pivot_longer(-c(State,Year,Abbrev,Code)) %>%
  left_join(states) %>%
  # Order the states
  mutate(State = factor(State,
                        levels=c("National Average",sort(unique(states$State)))))


# Add in the descriptive...
r1 <- r1 %>%
  left_join(vardesc, by = c("name" = "Variable Abbreviation")) %>%
  # Order it
  mutate(Variable = factor(Variable,levels=vardesc$Variable)) %>%
  arrange(Variable)

# 
#   # Now add in some text
#   mutate(Text = 
#            case_when(!is.na(`Decision Maker Takeaway`) & !is.na(Formula) ~
#                        paste0(
#                          "Variable definition: ",Definition,"\n",
#                          "Formula: ",Formula,"\n",
#                          "Decision maker takeaway: ",`Decision Maker Takeaway`,"\n",
#                          "Source: ",Source,"\n",
#                          "Data availability: ",Availability
#                        ),
#                      !is.na(`Decision Maker Takeaway`) & is.na(Formula) ~
#                        paste0(
#                          "Variable definition: ",Definition,"\n",
#                          "Decision maker takeaway: ",`Decision Maker Takeaway`,"\n",
#                          "Source: ",Source,"\n",
#                          "Data availability: ",Availability
#                        ),
#                      is.na(`Decision Maker Takeaway`) & is.na(Formula) ~
#                        paste0(
#                          "Variable definition: ",Definition,"\n",
#                          "Source: ",Source,"\n",
#                          "Data availability: ",Availability
#                        )
#            ))
  
# We will need to round out values for display 
# But where? We will want to plot exact and display rounded. 


```



<!-- We want tabs so we first need to have text as a heading, add the tabset feature here. Then anything else added as a heading under it will be under the tab! Arguments are .tabset-pills and .tabset-fade --> 

# {.tabset}

Use this page to explore 2014-2020 EHDI data. Variables or measurements are ordered with reported variables first, followed by calculated variables, and presented alphabetically within each group. Figures are interactive allowing you to hover for more information, zoom in/out, or download a plot as PNG (among the tools in upper right of each plot).


## State trends over time 

- Select the measurement at the top to see how states compare over time, 2014-2020.

- Hover over a line to highlight that state. 

- Double-click a state on the right to focus on that state. Click another to compare. Double-click to reset.

```{r}

#https://plotly-r.com/client-side-linking.html

# initializing a crosstalk shared data object  
plotdat <- highlight_key(r1)  # long data here

# Filter dropdown
question_filter <- crosstalk::filter_select(
   "filter", "Select a variable to examine",
   plotdat, ~Variable, multiple = F
)

# Plotting:
plot <-  plot_ly(plotdat, 
    x = ~Year, y = ~value, split = ~State, text = ~Variable,
    # type="scatter", 
    mode = "line",
    textposition = "top"
  ) %>%
  group_by(State) %>%
  # Add in some highlighting features to see if it works and increases interactivity.
    highlight(on = "plotly_hover", off = 'plotly_doubleclick',
              selectize = FALSE, # dropdown widget
              dynamic = FALSE,  # control highlighting color
              persistent = FALSE  # retain previous selections
    )

# Found this code here: https://stackoverflow.com/questions/64234585/selecting-a-default-value-in-an-r-plotly-plot-using-a-selectize-box-via-crosstal
# Will need to see if it works or not embedded in a website...
# Just putting things together for easy display:
shiny::tags$div(class = 'flexbox',
                question_filter,
                shiny::tags$br(),
                plot)


```

Data not available for every state in 2014-2020. See Data Availability Table for years of missing data for each state/variable.


## Annual map comparison

With this code we can map to a state the results of a variable in a year. Users can select a single variable and a single year.

```{r}

# In case the figures end up trying to speak with one another, we'll just make
# new objects here. 

# Establish a SharedData object to use. 
# The key here appears to be not having a key specified at all.
r1SD <- highlight_key(r1)

# Set up the widgets to be used for the mapping
widgets <- 
  # We can split the space occupied by each widget for easier viewing - total is 12
  bscols(widths = c(8,4),
         # Create a select filter for the variable
         filter_select("variableselect", "Please select measurement here", r1SD, ~Variable, multiple = F),
         # Create a select filter for the year - seems the only filter to select single year
         filter_select("yearselect", "Please select year here", r1SD, ~Year, multiple = F)
  )

# Now display the connected items - embed all in the bs rather than more objects
bscols(
  # div(align="right",margin="5000px 10px 10px 10px"),
  widths=(12),  # max is 12 so both elements should fit the width 
  widgets,
  # Plot a map of the SharedData object
  r1SD %>%
    plot_geo(locationmode = 'USA-states') %>% # Set the location to states
    # group_by(Variable,Year) %>%  # I don't think we need this here
    add_trace(locations=~Code, # must be state abbreviation
              z=~value,color=~value, # we want to see the map colored by the value
              text=~c(Year)) %>%  # nice way to verify when looking at a map that the year is as intended
    layout(
      # Change the view to be specific to the US
      geo = list(scope = 'usa',
                 projection = list(type = 'albers usa'),
                 lakecolor = toRGB('white')
      )) 
)


```

Data not available for every state in 2014-2020. See Data Availability Table for years of missing data for each state/variable. If a map does not populate, it is because data was not available for all states in that year. For example, there were no data available for total passed outpatient screening in 2014. 