---
output: 
    html_document:
      plots: 
        style: Normal
        align: left
      page_margins:
        bottom: 1
        top: 1
        right: 1
        left: 1
        header: 0.5
        footer: 0.5
        gutter: 0
      page_size:
        width: 8.5
        height: 11
        orient: "portrait"
    fig_caption: TRUE
    df_print: kable
    fig_height: 2.5
    fig_width: 4
always_allow_html: TRUE
editor_options: 
  chunk_output_type: console
---
[//]: # CSS style arguments

<style type="text/css">

@import url("https://fonts.googleapis.com/css?family=Open+Sans:400,400i,700,700i&display=swap");

h1, h2, h3, h4, h5, body, ul, ol, p, td, th {
font-family: 'Open Sans', sans-serif;

}


body{ /* Normal  */
      font-size: 20px;
      counter-reset:table figure;
  }

.table{
  width:auto;
  font-size:12px;
}

td, th{
  padding-left:10px;
  text-align: right;
  font-family: 'Open Sans', sans-serif;
}

caption::before{
  counter-increment: table;
  content: "Table " counter(table) ": ";
}

.caption::before{
  counter-increment: figure;
  content: "Figure " counter(figure) ": ";
}

caption, .caption{
  font-style:italic;
  font-size: 16px;
  margin-top:0.5em;
  margin-bottom:0.5em;
  width:80%;
  text-align: left;
}

#TOC {
  font-size: 17px;
  width: 100%;
}

</style>

```{r setup, include=FALSE}

# You can set a default figure size here so you don't have to customize every time
knitr::opts_chunk$set(fig.width=8, fig.height=6, warning=FALSE, message=FALSE, cache=FALSE, echo=FALSE)

```

```{r}

# '# PROLOG   ##################################################################'
# '#                                                                           #'
# '# PROJECT: EHDI                                                             #'
# '# PURPOSE: To create visualizations for earlyhearinglossdata website        #'
# '# DIR:     Box\CPHSS\EHDI Seeser\Data\Scripts                               #'
# '# RPRJ:    Box\CPHSS\EHDI Seeser\Data\Data.Rproj                            #'
# '# DATA:    Box\CPHSS\EHDI Seeser\Data\website_ready_data                    #'
# '# AUTHOR:  Veronica L Chaitan                                               #'
# '# CREATED: Aug 09, 2023                                                     #'
# '# LATEST:  SEP 07, 2023                                                     #'
# '# NOTES:                                                                    #'
# '#                                                                           #'
# '# PROLOG   ##################################################################'

library(readxl)
# library(htmltools)
# library(crosstalk)
# library(plotly)
library(kableExtra)
library(magrittr)
library(tidyverse)

# for NA in kable
options(knitr.kable.NA = "")

# Theme settings
# theme_set(theme_minimal()) - doesn't carry over across chunks in RMD
# In general
mytheme <- theme_minimal() + 
  theme(text = element_text(size=11, color="gray23"),
        panel.grid = element_blank(),
        axis.text.x = element_text(size=8, color="gray23"),
        axis.text.y = element_text(size=10, color="gray23"),
        axis.title = element_blank(),
        plot.title = element_blank(),
        legend.position = "top",
        legend.title = element_blank())

# Descriptive table information
vardesc <- read_xlsx("../website_ready_data/variableDescriptionsForWebsite_v1.xlsx") 

# In this case keep just the calculated variables
vardesc <- vardesc %>%
  filter(Source == "Calculated from reported data") %>%
  select(-c(Source,Availability)) %>%
  mutate(Formula = case_when(Formula == "Tscr - (PaInNoOut + PaInPaOut + PaInReOut + NoInPaOut + NoInReOut) OR ReInNoOut + ReInReOut + ReInPaOut + ReInStDia" ~
                               "Tscr - (PaInNoOut + PaInPaOut + PaInReOut + NoInPaOut + NoInReOut) <br> OR <br>  ReInNoOut + ReInReOut + ReInPaOut + ReInStDia",
                             TRUE ~ Formula))

```

```{r}

kable(vardesc,
      # Align all text to the left
      align="l")  %>%
  # Let's identify the variables a little better
  column_spec(1, bold = T) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive","bordered"),
                full_width = T, fixed_thead = TRUE)

```